Properties of Winning Iterated Prisoner's Dilemma Strategies.

### 2020-04-25 paper/main.tex
fixes discussion on sse distributions and CD to C rates

The distributions of the SSE across the tournament types suggest that successful
strategies exhibit some extortionate behaviour, but not constantly.
ZDs are a set of strategies that are often envious as they try to exploit their
opponents. The winners of the tournaments considered in this work are
envious, but not as much as many ZDs. This highlights why TFT's early tournament
success fails to generalize -- it never attempts to defect against a cooperating
or exploitable opponent (e.g. Alternator). Moreover, many of the strategies in
the library will not tolerate exploitation attempts. A clever strategy can
achieve mutual cooperation with stronger strategies while also being able to
exploit weaker strategies. This is why ZDs fail to appear in the tops
ranks -- they try to exploit all opponents and cannot actively adapt back to
mutual cooperation against stronger strategies, which requires more depth of memory.
\footnote{Note that ZDs also tend to perform poorly in population games for
a similar reason: they attempt to exploit other players using ZDs, failing to
form a cooperative subpopulation. This makes them good invaders but poor resisters of invasion.}

@@

The distributions of the \(CD\) to \(C\) rate evaluate the behaviour of a
successful strategy after its opponent has defected against it. In standard
tournaments it was observed that a successful strategy reciprocates with a
probability of 0.5.
This leads to the recommendation of needing to be somewhat provocable.
This is distinct between the tournament types. In
tournaments with noise a strategy is less likely to cooperate following a
defection compared to standard tournaments, and in probabilistic ending
tournaments a strategy will reciprocate a defection. In a setting that the type
of the tournament can vary between all the examined types a winning strategy
would reciprocate on average with a probability of 0.58.

@@

>>>>

The distributions of the SSE across the tournament types suggest that successful
strategies exhibit some extortionate behaviour, but not constantly.
ZDs are a set of strategies that are often envious as they try to exploit their
opponents. The winners of the tournaments considered in this work are
envious, but not as much as many ZDs.
Though the exact interactions between the matches have not been recorded here,
the work of~\cite{Harper2017} which introduced the trained strategies that
appeared in the top ranked strategies of Section~\ref{section:top_performances}
did. In~\cite{Harper2017} it was shown that clever strategies managed to achieve
mutual cooperation with stronger strategies whilst exploiting the weaker
strategies. This could potentially be what is happening with the clever winners
of our analysis, and would explain the SSE distributions. This could also
be the reason why ZDs fail to appear in the tops ranks -- they try to exploit
all opponents and cannot actively adapt back to mutual cooperation against
stronger strategies, which requires more depth of memory. \footnote{Note that
ZDs also tend to perform poorly in population games for a similar reason: they
attempt to exploit other players using ZDs, failing to form a cooperative
subpopulation. This makes them good invaders but poor resisters of invasion.}

@@

The distributions of the \(CD\) to \(C\) rate evaluate the behaviour of a
successful strategy after its opponent has defected against it. In standard
tournaments it was observed that a successful strategy reciprocates with a
probability of 0.5, and in a setting that the type
of the tournament can vary between all the examined types a winning strategy
would reciprocate on average with a probability of 0.58. In
tournaments with noise a strategy is less likely to cooperate following a
defection compared to standard tournaments, and in probabilistic ending
tournaments a strategy will reciprocate a defection.
This leads to revisit the recommendation of being provocable to defections made
by R. Axerlod. In fact only in tournament that are not long a strategy should
be too provocable, in the rest of the settings a strategy should be more
generous.

@@

This highlights why TFT's early tournament
success fails to generalize -- it never attempts to defect against a cooperating
or exploitable opponent (e.g. Alternator).
